Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-07-28 Documents/Paper/ms.tex
More citations

\section{Sinusoidal example}
In this section we demonstrate a seemingly simple example which exhibits
a phase transition, making a standard MCMC approach difficult. Suppose
a signal is composed of $N$ sinusoids, of different periods, amplitudes,
and phases. The signal is observed at various times $\{t_i\}_{i=1}^N$ with
noise, and we want to use the resulting data to infer the number of sinusoids
$N$, along with the periods $\{T_i\}_{i=1}^N$, amplitudes $\{A_i\}_{i=1}^N$,
and phases $\{\phi_i\}_{i=1}^N$.
This kind of model has many applications, and has been solved analytically
under certain sets of assumptions \citep[see e.g.][]{bretthorst}. Similar
models have been used in many different fields
\citep[e.g.][]{}. Note that this problem is also very closely related to the
problem of detecting exoplanet signals in radial velocity data, which has
attracted a lot of interest
\citep[e.g.][]{2007ApJ...654..551B, gregory, fengji, 2011MNRAS.415.3462F}.

@@

@@

>>>>

\section{Sinusoidal example}
In this section we demonstrate a seemingly simple example which exhibits
a phase transition, making a standard MCMC approach difficult. Suppose
a signal is composed of $N$ sinusoids, of different periods, amplitudes,
and phases. The signal is observed at various times $\{t_i\}_{i=1}^N$ with
noise, and we want to use the resulting data to infer the number of sinusoids
$N$, along with the periods $\{T_i\}_{i=1}^N$, amplitudes $\{A_i\}_{i=1}^N$,
and phases $\{\phi_i\}_{i=1}^N$.
This kind of model has many applications, and has been solved analytically
under certain sets of assumptions \citep[see e.g.][]{bretthorst}. Similar
models have been used in many different fields
\citep[e.g.][]{2005PhRvD..72b2001U, 2007ApJ...654..551B, 2003AIPC..659....3B}.
Note that this problem is also very closely related to the
problem of detecting exoplanet signals in radial velocity data, which has
attracted a lot of research attention in recent years
\citep[e.g.][]{2007ApJ...654..551B, gregory, fengji, 2011MNRAS.415.3462F}.

@@

\bibitem[Bretthorst(2003)]{2003AIPC..659....3B} Bretthorst, G.~L.\ 2003.\ 
Frequency Estimation, Multiple Stationary Nonsinusoidal Resonances With 
Trend.\ Bayesian Inference and Maximum Entropy Methods in Science and 
Engineering 659, 3-22.

@@

\bibitem[Umst{\"a}tter et al.(2005)]{2005PhRvD..72b2001U} Umst{\"a}tter, 
R., Christensen, N., Hendry, M., Meyer, R., Simha, V., Veitch, J., 
Vigeland, S., Woan, G.\ 2005.\ Bayesian modeling of source confusion in 
LISA data.\ Physical Review D 72, 022001.
